---
title: "Cabbages"
author: "Louie A"
date: "6/5/2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(ucdavis1,aes(x=Sex,y=dadheight))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

```{r}
# Create a boxplot using ggplot2
ggplot(veggy, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  labs(title = "VitC Boxplot by Cult", x = "Cult", y = "VitC")
```

If you look one of the boxes are completely above the other box by what it looks like %50.
They are completely separated from each other. Most likely going to find a statistical difference between the two 


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```

The average amount of C39 is 51.5. while c52 is at 64.4. c52 is bigger than c39, it is disjointed. This is in a numerical form of the average mean and median.  

## Inferential Results


<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

The probably of getting the result is .00000003405. In which is incredibly small. the math between c39 and c52 is low that a might happen but is unlikely that it will ever happen. we reject there is a theory on there being a difference.  
  

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Today we figured out how to use a plot point with the help of chat GPT. We gave results on this vitamin C problem and concluded that there is a difference between the tow but the results were small.  


